---
title: 'Lab Practical: Part 2'
author: "Sammy Ko"
output:
  html_document:
    df_print: paged
---

**Load libraries here** 
```{r}
#You can code here
list.files()
df <- read.csv("Hummingbird.csv", header= TRUE)
```



**Q1: Write out a hypothesis and prediction for this comparison (2 points) **
[The average beak size of Filt's Hummingbird is larger than the average beak size of Anna's Hummingbird.
Therefore, Filt's Hummingbird is a different species than Anna's Hummingbird.]


**Q2: Load the Hummingbird data into R using the file name "Hummingbird" and view the first 6 lines using the head() function (2 points)**
```{r}
#You can code here
head(df)

```

***Use the R dataset "trees" for Q3-5***

**Q3: Evaluate the relationshp between height and diamter of tree using an appropriate statistical test (2 points).**

```{r}
#You can code here! 
attach(trees)
View(trees)
cor.test(Height,Girth)
```

**Q4: Create a publication quality figure of these data. (2 points) **
```{r}
#You can code here! 
library(ggplot2)
ggplot(trees, aes(Height,Girth)) + geom_point() + labs(x="Height ", y="Girth") + geom_smooth(method = "lm")+ theme_classic()
```

**Q5: Write a properly worded results statement. (2 points)**
[There is a significant positive correlation between the height and the girth of the trees(r=0.5192801).]


***Use the R dataset "PlantGrowth" for Q6-8***

**Q6: Evaluate the relationship between treatment and plant yield using an appropriate statistical test (2 points)**

```{r}
#You can code here
attach(PlantGrowth)
View(PlantGrowth)
anova <- aov(weight~group)
summary(anova)
```

**Q7: Create a publication quality figure of these data (2 points)**

```{r}
#You can code here
ggplot(PlantGrowth, aes(group,weight)) + geom_boxplot() + labs(x="Treatment groups", y="Weight") + theme_classic()
```

**Q8: Write a properly worded results statement. (2 points)**
[We reject the null hypothesis, and there is a significant relationship between treatment conditions and the weight of plants (p-value=0.0159).]


